msb106_assignment

### 2024-01-15 msb106_assignment.qmd
Lagt inn oppgaveteksten

The objective of this assignment is to provide a understanding of some of the potential drivers influencing urban-rural divide in Europe.
We will explore the impact of factors defining this division, like local labour market conditions, affect patterns of population distribution and job creation across different European landscapes.

@@

The first part will present an overview of population growth dynamics in various European regions, establishing a solid context for the advanced analyses that follow.

@@

In the second part, we will extend the data collected in the first part by incorporating additional economic factors.
Our analysis will delve into how these factors correlate with population growth in different regions, utilizing the classification methodology detailed in Chapter 5 of Andersson, Håkansson, and Thorsen (2023).

>>>>

The aim of this assignment is to provide an understanding of some of the potential drivers contributing to the urban-rural divide in Europe.
We will delve into the influence of factors shaping this division, such as local labour market conditions, affect patterns of population distribution and job creation across different European landscapes.

@@

The first part presents an overview of the data collection process, followed by an analysis of the population growth dynamics in various European regions.

@@

In the second part, we will extend the data collected in the first part by incorporating additional economic factors.
Our analysis will focus on how these factors correlate with population growth in different regions, employing the classification methodology detailed in Chapter 5 of Andersson, Håkansson, and Thorsen (2023).
